What is disputed on the web?

### 2010-02-01 papers/wicow_claimfinder/claimfinder.tex
More changes

We built a statitical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. We used a simple Bayesian classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.

>>>>

We built a statitical classifier that attempts to automatically determine whether any given string matched by a pattern is an unambiguous disputed claim. We used a simple Naive Bayes classifier whose features were the words that were present in the string, the parts of speech that were present in the string, and the identity and pos-tag of the first and second words.
